Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/evalrelate.tex
More on Implementation

\section{Implementation Details}

@@

\subsection{Program Slicer}

>>>>

\subsection{Implementation Details}

@@

\subsubsection{Program Instrumenter}

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traverse this tree and collect informations about location of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

\subsubsection{Program Slicer}
